---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# educationr2
### Written by Roxane Marine Van Olden Barneveld, Killian Harnett, Krisra Ritina and Ronan Lambe

<!-- badges: start -->
<!-- badges: end -->

educationr2 includes a data set named students consisting of the marks secured by the students in mathematics, reading and writing exams, along with information on gender, ethnicity, parental education level, lunch type, and participation in a test preparation course. It allows for analyzing the influence of these factors on academic performance. Three functions include

  1. `prepare_student_data()` method: this prepares the data. It tidys into a clear readable and usable format
  
  2. `plot_student_scores()` method for producing nice visualizations based on `ggplot2`.
  
  3. `summary.StudentData()` this method calculations summary statistics for (mean median etc) for the data set 



## Installation

You can install the development version of educationr2 from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("roxane-vnldn/educationr2")
```

## Example

This is a basic example which shows you how to use educationr2 to interact with the students dataset:

Firstly prepare the data 
```{r example}
library(educationr2)

data <- prepare_student_data(students)
head(data)
```

Now to visually display the data
```{r example2}

plot.StudentData(data, "gender", "barplot")
```
Or we can get statistial summarys 

```{r example3}

summary.StudentData(data, group_var = c("gender", "lunch"), summary_func = median)

```


