---
title: "educationr2"
output: 
  bookdown::html_document2:
      base_format: rmarkdown::html_vignette
      fig_caption: yes
      number_sections: no
urlcolor: blue
header-includes:
  \usepackage{amsmath}
vignette: >
  %\VignetteIndexEntry{educationr2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{bookdown}
  %\VignetteDepends{ggplot2}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 7,
  fig.height = 5,
  fig.align = "center",
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE}
library(educationr2)
```


## Introduction

educationr2 takes a data set consisting of the marks secured by the students in mathematics, reading and writing exams, along with information on gender, ethnicity, parental education level, lunch type, and participation in a test preparation course. It allows for analyzing the influence of these factors on academic performance. Three functions include

  1. `prepare_student_data()` method: this prepares the data. It tidys into a clear readable and usable format
  
  2. `plot.StudentData()` method for producing nice visualizations based on `ggplot2`.
  
  3. `summary.StudentData()` this method calculations summary statistics for (mean median etc) for the data set 
  
This vignette demonstrates a typical workflow using the educationr2 package, guiding you through data preparation, visualization, and summarisation.  

## Installation

You can install the development version of educationr2 from
[GitHub](https://github.com/) with:

``` {r, eval=FALSE}
install.packages("devtools")
devtools::install_github("roxane-vnldn/educationr2")
```

then to load the package you simply use

```{r, eval=FALSE}
library(educationr2)
```


## 'prepare_student_data()'


The `prepare_student_data()` function processes and tidies the student dataset. It handles missing values, converts non-score variables to factors, and optionally standardizes numeric score variables.

### Example Usage

```{r}
students <- data.frame(
  math.score = c(72, 69, NA, 47, 76),
  reading.score = c(72, 90, 95, 57, 78),
  writing.score = c(74, 88, 93, 44, 75),
  gender = c("female", "female", "female", "male", "male"),
  lunch = c("standard", "free/reduced", "standard", "free/reduced", "standard")
)

tidy_data <- prepare_student_data(students, scale = TRUE, handle_missing = "mean")
tidy_data
```





The prepare_student_data() function prepares and cleans the input dataset, ensuring it is ready for analysis. It organizes the data into a tidy format, standardizes column names, and ensures data consistency.



## 'plot.StudentData()'


The `plot.StudentData()` method generates visualizations comparing subject scores against a chosen categorical variable. Supported plot types include `"boxplot"`, `"violin"`, and `"barplot"`.

### Example Usage

```{r, echo=FALSE, results='hide'}
data <- prepare_student_data(students, scale = FALSE)
p <- plot.StudentData(data, categorical_var = "gender", plot_type = "boxplot")
```

```{r}
plot.StudentData(data, categorical_var = "gender", plot_type = "boxplot")
```

You can replace `"boxplot"` with `"violin"` or `"barplot"` for different visualizations.


## 'summary.StudentData()'

The `summary.StudentData()` function computes summary statistics (e.g., mean, median, max) for the student dataset, grouped by one or more categorical variables.

### Example Usage

```{r}
summary_stats <- summary.StudentData(
  obj = tidy_data,
  group_var = c("gender", "lunch"),
  summary_func = median
)
summary_stats
```

This calculates the median scores for each combination of `gender` and `lunch` categories.

## Workflow Example

Here’s a complete example demonstrating the workflow:

1. Prepare the data:

```{r}
processed_data <- prepare_student_data(students, scale = FALSE)
```

2. Visualize the data:

```{r}
plot.StudentData(processed_data, categorical_var = "lunch", plot_type = "violin")
```

3. Compute summary statistics:

```{r}
summary_stats <- summary.StudentData(processed_data, group_var = "gender", summary_func = mean)
summary_stats
```

These steps highlight how __educationr2__ simplifies the analysis of student performance data. 


