---
title: "educationr2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(educationr2)
```


educationr2 takes a data set consisting of the marks secured by the students in mathematics, reading and writing exams, along with information on gender, ethnicity, parental education level, lunch type, and participation in a test preparation course. It allows for analyzing the influence of these factors on academic performance. Three functions include

  1. `prepare_student_data()` method: this prepares the data. It tidys into a clear readable and usable format
  
  2. `plot_student_scores()` method for producing nice visualizations based on `ggplot2`.
  
  3. `summary.StudentData()` this method calculations summary statistics for (mean median etc) for the data set 

## Installation

